---
title: "Data Wrangling Excercise 2"
author: "Eric"
date: "April 3, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load and Read CSV



```{r cars}
library(readxl)
library(dplyr)
titanic_original<-read_excel('titanic3.xls')
titanic<-tbl_df(titanic_original)

```

## Check the dataframe



```{}
View(titanic)

```


## Embark missing value

```{embark missing value}
#emabark missing value

titanic$embarked[is.na(titanic$embarked)]<-'S'
```

## Clean up age missing value 

Replace missing value of age with mean.
It will change the distribution of the population; however it won't change the mean. 
I think it's okay to use the mean to fill the null unless you're trying to get the mode. 

```{}
#age missing value
m<-mean(titanic$age,na.rm=TRUE)
titanic$age[is.na(titanic$age)]<-m
```

boat missing value

```{}
#boat missing value
titanic$boat[is.na(titanic$boat)]<-'None'

```

cabin missing value
I do not think it is necessary to fill the empty value here since at the time not everyone on the ship is rich enough to afford a cabin.
Some might not have a cabin and filling the cabin number with a filled value will twist the fact.


Create has_cabin_number
```{}
#has_cabin_number 
titanic$has_cabin_number[is.na(titanic$cabin)]<-0
titanic$has_cabin_number[!(is.na(titanic$cabin))]<-1
```